Notes of Quantum Field Theory in a Nutshell

### 2016-08-16 Complex Geometry - index/Complex Geometry - index.tex
Update QFT in nutshell's notes.
Daily update. New resource for QFT.
Update QFT in a nutshell, Complex Geometry notes. Improved git-push.bat script for visual echo.

    \textcolor{blue}{hermitian form $(,)$}:=$<,>-i\cdot\omega$.
    (\textbf{pp.30})
\section{2.Complex Manifolds}

@@

\begin{thebibliography}{1}
	\bibitem{book} Complex Geometry
\end{thebibliography}
\part{License}
The entire content of this work (including the source code
for TeX files and the generated PDF documents) by 
Hongxiang Chen (nicknamed we.taper, or just Taper) is
licensed under a 
\href{http://creativecommons.org/licenses/by-nc-sa/4.0/}{Creative 
Commons Attribution-NonCommercial-ShareAlike 4.0 International 
License}. Permissions beyond the scope of this 
license may be available at \url{mailto:we.taper[at]gmail[dot]com}.
\end{document}

>>>>

    \textcolor{blue}{hermitian form $(,)$}:=$<,>-i\cdot\omega$.
    (\textbf{pp.30})

    \textcolor{blue}{Lefschetz operator $L$}:
        $\bigwedge^* V^*_{\mathbb{C}}\to
    \wedge^* V_{\mathbb{C}}^*$, given by $\alpha\to\omega\wedge\alpha$.
    (\textbf{pp.31})

    \textcolor{blue}{Hodge star $*$-operator}: $\alpha\wedge *\beta=
        \langle\alpha,\beta\rangle \cdot \text{vol}$.
    (\textbf{pp.33})

    \textcolor{blue}{dual Lefschetz operator $\Lambda$}:
        $\langle\Lambda\alpha,\beta\rangle =\langle\alpha,L\beta\rangle$,
        degree $-2$, bidegree $(-1,-1)$, $\Lambda=*^{-1}\circ L\circ *$.
    (\textbf{pp.33 to 34})

    \textcolor{blue}{Counting operator $H$}:
        $H=\sum_{k=0}^{2n}(k-n)\cdot\prod^k$, 
        where $\text{dim}_{\mathbb{R}}=2n$.
    (\textbf{pp.34})

    \textcolor{blue}{commutator [A,B]}:$=A\circ B-B\circ A$.
    (\textbf{pp.34})

\paragraph{Commutators}
$$[H,L]=2L,\text{ } [H,\Lambda]=-2\Lambda,\text{ } [L,\Lambda]=H.$$
(\textbf{pp.34})

$$[L^i,\Lambda](\alpha)= i(k-n+i-1)L^{i-1}(\alpha),\text{for all}
    \alpha\in\bigwedge^k V^*$$
(\textbf{pp.35})

    \textcolor{blue}{primitive element} in $\bigwedge^kV^*$:
        $\alpha$ is primitive if and only if $\Lambda\alpha=0$.
    (\textbf{pp.36})

    \textcolor{blue}{$P^k$} $\subset\bigwedge^kV^*$: is the subspace
    of all primitive elements.
    (\textbf{pp.36})
\section{2.Complex Manifolds}

@@

\begin{prop}[Lefschetz decomposition]
    There exists a direct sum decomposition of the form:
    \begin{align}
        \bigwedge^kV^* = \bigoplus_{i\geq 0} L^i(P^{k-2i})
    \end{align}
    Also, $P^k={\alpha\in \bigwedge^k V^*|L^{n-k+1}\alpha=0}$, for
    $k\leq n$. Naturally $P^k=0$ for $k>0$.

    We also have several morphisms induced by $L$, which is illustrated
    in the following graph adapted from the book:

    \begin{figure}[H]
        \centering
        \includegraphics[width=1.3\linewidth]{pics/{prop-1.2.30-pp.36}.pdf}
        \caption{Morphisms}
    \end{figure}
\end{prop}
(\textbf{pp.36 of \cite{book}})
\begin{thebibliography}{1}
	\bibitem{book} Complex Geometry
\end{thebibliography}
\part{License}
The entire content of this work (including the source code
for TeX files and the generated PDF documents) by 
Hongxiang Chen (nicknamed we.taper, or just Taper) is
licensed under a 
\href{http://creativecommons.org/licenses/by-nc-sa/4.0/}{Creative 
Commons Attribution-NonCommercial-ShareAlike 4.0 International 
License}. Permissions beyond the scope of this 
license may be available at \url{mailto:we.taper[at]gmail[dot]com}.
\end{document}

### 2016-08-16 QFT/Notes of QFT in a Nutshell/Notes of QFT in a Nutshell.tex
Update QFT in a nutshell, Complex Geometry notes. Improved git-push.bat script for visual echo.

@@

where:
\begin{align}
    \int Dq(t) \equiv \lim_{N\to \infty} 
    \left( \frac{-im}{2\pi \delta t}\right)^{N/2}
    \left( \prod_{k=1}^{N-1} \int dq_k \right)
\end{align}
It notes that when $H=\hat{p}^2/2m + V(\hat{q})$, the final result
would have been:
\begin{align}
    \label{eq:QFT_in_a_Nutshell_Part_I.2.TransProbability}
    \braket{q_F|e^{-iHT}|q_I} &= \int Dq(t) 
        e^{i\int_0^T dt \frac{1}{2}m \dot{q}^2 - V(q)}
        \nonumber \\
        &=\int Dq(t) e^{i \int_0^T dt L(\dot{q}, q)}
\end{align}
where $L$ is the Lagrangian of the system.

@@

The value \(\braket{0|e^{-iHT}|0}\) is denoted $Z$. This part
mentions that one often effect a change of coordinate
$t \to -it$, called \textit{Wick rotation}, to obtain:
\begin{align}
    Z = \int Dq(t) e^{-\int_0^T dt H(\dot{q},q)}
\end{align}
where $H$ is the Hamiltonian of the system.
The mathematical rigorous aspect is often ignored.

@@

\paragraph{Mattress in continuum limit} It start with taking the
limit of lattice spacing $l\to 0$, aiming to write down the field
equation from the mattress perspective. The process is transparant
and neatly summarized in the "promotion table" on page 19:

@@

Also it is customary to write $d = D + 1$ and speak of a 
$(D + 1)$-dimensional spacetime. When $D=0$, quantum
field theory reduces to normal quantum mechanics,
which deal with only a point (in the mattress
sense, we have only one particle).

@@

\paragraph{Vacuum and Response}

@@

Here he centers at the the Lagrangian
\begin{align}
    \mathcal{L}(\phi)=\frac{1}{2}\left( (\partial\phi)^2-m^2\phi^2\right)
\end{align}
The corresponding theory is called the \textbf{free} or 
\textbf{Guassian theory}. Using 
\ref{eq:QFT_in_a_Nutshell_Part_I.3.classicalFieldEq}, one can easily
obtain the Klein-Gorden equation:
\begin{align}
    (\partial^2+m^2)\phi=0
\end{align}
The plain wave solution is of the form:
\begin{align}
    \omega^2=\vec{k}^2+m^2
\end{align}
He notes that by transfer back to the SI unit, one will
recognize above equations the same as the $E=mc^2$ identity.

@@

We also denote the exponent in \ref{eq:QFT_in_a_Nutshell_Part_I.3.3}
as $W(J)$. So:
\begin{align}
    \label{eq:}
    W(J) = -\frac{1}{2} \int\int d^4x d^4y J(x)D(x-y)J(y) \\
    Z= \mathcal{C}e^{iW(J)}
\end{align}

@@

With the Fourier transformation, several physical properties
could be extrated from $W(J)$. The Fourier transformed $W(J)$ is:
\begin{align}
    W(J) = -\frac{1}{2}\int \frac{d^4}{(2\pi)^4}J(k)^*
        \frac{1}{k^2-m^2+i\epsilon}J(k)
\end{align}
If separating $J$ into $J(x)=J_1(x)+J_2(x)$, then naturally, the
Fourier transformed calculation will include terms of the form:
$J^*_1J_1,J^*_1J_2,J^*_2J_1,J^*_2J_2$. We see that the denominator
in $W(J)$ contains $k^2-m^2$. Somehow the author wants to argue that
the term $J^*_2J_1$ describes the influence of a particle of mass $m$
propagating from the source $1$ to the sink $2$. But his language is loose.

@@

\paragraph{Origin of force}
The energy calculated above, and the previous \textit{sink and source}
interpretation, lead us to believe that force is the result of an
exchange of particles.

@@

\paragraph{Bypassing Maxwell}
% TODO stopped here.
I am not sure what to write here, since I lost grip of which field
the author is trying to calculate: meson of spin 1? or phonton?.
\chapter{Bibliography}
\begin{thebibliography}{1}
	\bibitem{zee} A. Zee. Quantum Field Theory in a Nutshell
		2ed. PUP.
\end{thebibliography}
\chapter{License}
The entire content of this work (including the source code
for TeX files and the generated PDF documents) by 
Hongxiang Chen (nicknamed we.taper, or just Taper) is
licensed under a 
\href{http://creativecommons.org/licenses/by-nc-sa/4.0/}{Creative 
	Commons Attribution-NonCommercial-ShareAlike 4.0 International 
	License}. Permissions beyond the scope of this 
license may be available at \url{mailto:we.taper[at]gmail[dot]com}.

\end{document}

>>>>

\usepackage{nomencl} % For a index of symbols.
\makenomenclature % For a index of symbols.

@@

where:
\begin{align}
    \int Dq(t) \equiv \lim_{N\to \infty} 
    \left( \frac{-im}{2\pi \delta t}\right)^{N/2}
    \left( \prod_{k=1}^{N-1} \int dq_k \right)
\end{align}
\nomenclature{$\int Dq(t)$}{\nomrefpage}
It notes that when $H=\hat{p}^2/2m + V(\hat{q})$, the final result
would have been:
\begin{align}
    \label{eq:QFT_in_a_Nutshell_Part_I.2.TransProbability}
    \braket{q_F|e^{-iHT}|q_I} &= \int Dq(t) 
        e^{i\int_0^T dt \frac{1}{2}m \dot{q}^2 - V(q)}
        \nonumber \\
        &=\int Dq(t) e^{i \int_0^T dt L(\dot{q}, q)}
\end{align}
where $L$ is the Lagrangian of the system.

@@

We define:
\begin{align}
    Z\equiv \braket{0|e^{-iHT}|0}
\end{align}
\nomenclature{$Z$}{\nomrefpage}

This part mentions that one often effect a change of coordinate
$t \to -it$, called \textit{Wick rotation}, to obtain:
\begin{align}
    Z = \int Dq(t) e^{-\int_0^T dt H(\dot{q},q)}
\end{align}
where $H$ is the Hamiltonian of the system.
The mathematical rigorous aspect is often ignored.

@@

\paragraph{Mattress in continuum limit}

\footnote{
    \textbf{Note}: Here and afterwards, the author suppresses the factor 
    $\braket{0|q_f} \braket{q_I|0}$.
}

It start with taking the
limit of lattice spacing $l\to 0$, aiming to write down the field
equation from the mattress perspective. The process is transparant
and neatly summarized in the "promotion table" on page 19:

@@

Also it is customary to write $d = D + 1$ and speak of a 
$(D + 1)$-dimensional spacetime
\nomenclature{$(D + 1)$-dimensional spacetime}{\nomrefpage}. 
When $D=0$, quantum field theory reduces to normal quantum mechanics,
which deal with only a point (in the mattress
sense, we have only one particle).

@@

\paragraph{Vacuum and (Linear) Response}

@@

Here he centers at the the Lagrangian
\begin{align}
    \mathcal{L}(\phi)=\frac{1}{2}\left( (\partial\phi)^2-m^2\phi^2\right)
\end{align}
The corresponding theory is called the \textbf{free} or 
\textbf{Guassian theory}. Using 
\ref{eq:QFT_in_a_Nutshell_Part_I.3.classicalFieldEq}, one can easily
obtain the Klein-Gorden equation:
\begin{align}
    (\partial^2+m^2)\phi=0
\end{align}
The plain wave solution 
    $\phi(\vec{x},t)=e^{i(\omega t-\vec{k}\cdot\vec{x})}$ 
has the property:
\begin{align}
    \omega^2=\vec{k}^2+m^2
\end{align}
He notes that by transfer back to the SI unit, one will
recognize above equations the same as the $E=mc^2$ identity.

@@

We also denote the exponent in \ref{eq:QFT_in_a_Nutshell_Part_I.3.3}
as $W(J)$ \nomenclature{$W(J)$}{\nomrefpage}. So:
\begin{align}
    \label{eq:}
    W(J) = -\frac{1}{2} \int\int d^4x d^4y J(x)D(x-y)J(y) \\
    Z= \mathcal{C}e^{iW(J)}
\end{align}

@@

With the Fourier transformation, several physical properties
could be extrated from $W(J)$. The Fourier transformed $W(J)$
\nomenclature{Fourier transformed $W(J)$}{\nomrefpage} is:
\begin{align}
    W(J) = -\frac{1}{2}\int \frac{d^4}{(2\pi)^4}J(k)^*
        \frac{1}{k^2-m^2+i\epsilon}J(k)
\end{align}
If separating $J$ into $J(x)=J_1(x)+J_2(x)$, then naturally, the
Fourier transformed calculation will include terms of the form:
$J^*_1J_1,J^*_1J_2,J^*_2J_1,J^*_2J_2$. We see that the denominator
in $W(J)$ contains $k^2-m^2$. Somehow the author wants to argue that
the term $J^*_2J_1$ describes the influence of a particle of mass $m$
propagating from the source $1$ to the sink $2$. But his language is loose.

@@

\textbf{Note} that the field $\phi$ used here is like the field used
by Yukawa. The Yukawa model correctly describes the field of
$\pi$ meson, also called pion.
\nomenclature{$\pi$ meson}{ also called pion\nomrefpage}
\paragraph{Origin of force}
The energy calculated above, and the previous \textit{sink and source}
interpretation, lead us to believe that force is the result of an
exchange of particles.

@@

\paragraph{Bypassing Maxwell}
% TODO stopped here.

\paragraph{Unclear Points} Marked in the book. Especially, where
in the calculatioin above shows that the field is of a spin $1$
or a spin $2$ meson?

\chapter{Bibliography}
\begin{thebibliography}{1}
	\bibitem{zee} A. Zee. Quantum Field Theory in a Nutshell
		2ed. PUP.
\end{thebibliography}
\chapter{License}
The entire content of this work (including the source code
for TeX files and the generated PDF documents) by 
Hongxiang Chen (nicknamed we.taper, or just Taper) is
licensed under a 
\href{http://creativecommons.org/licenses/by-nc-sa/4.0/}{Creative 
	Commons Attribution-NonCommercial-ShareAlike 4.0 International 
	License}. Permissions beyond the scope of this 
license may be available at \url{mailto:we.taper[at]gmail[dot]com}.

% For a list of symbols.
\printnomenclature
\end{document}
